### 2023-02-03 paper-reviews/papers-2023.tex
Add VMM trands article

>>>>

\section*{Virtual Machines}
\begin{itemize*}
    \item \cite{Rosenblum:VMM-trends:2005}:

    The article includes a very concise VMM history and some basic techniques like \textit{shadow paging}. Strict focus of the article is on VMware's solutions of that time. There described one interesting paravirtualization idea I didn't know about before --- \textit{ballon process} running inside a Guest OS and communicating with the VMM. The process can allocated a bunch of memory thus forcing the Guest OS to use its knowledge about other processes to page unused memory out. VMM thus can also page out this memory and then reclaim the memory used by the \textit{ballon process} - nice trick.
\emd{itemize*}
